### 2021-08-04 doc/thesis/chapters/results.tex
axi-lite regs

@@

LED Control, Build Information Register, Pass-Through
\subsubsection{FIR Filter}

@@

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Integration}
% IP generation and integration into Vivado
% Issue: HLS driver import did not work - Vivado SDK is a mess (bad UI based on Eclipse, has bugs, no error output, etc...)
%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports

>>>>

This interface is used to control IP settings and to read status information.
Similar to the previous AXI Stream interface, also this AXI4-Lite memory-mapped interface is automatically generated by HLS, while this has to be done manually in VHDL.
To create this process more efficiently and extendable, a Python script is used, which can also automatically generate VHDL code for the registers' memory map.
This turns out to be a multiplicator in productivity for the implementation of registers.
The register generator script was previously used in projects and is therefor already well-known and tested before it is used in this project.
However, the VHDL code only represents one part of the interface -- the second part is the firmware driver that is used in the application software.
Even though the register generator script also generates a \cplusplus\ header file that includes several address offset definitions of the registers, the actual driver functions need to be implemented manually.
Several files need to be integrated into a pre-defined folder structure, in order to enable a correct integration of the IP in a Vivado block diagram.\\

Again, the amount of manual steps in the VHDL implementation are clearly represented in the number of hours that are spent.

% TODO: mention figure out of read-only and read-write types (pointer/reference)
% TODO: mention testbench (vhdl: support block, hls: simple access to variable)

@@

Once the AXI4-Lite memory-mapped interface's main functionality is implemented, further registers can be added.
In the specific implementation for this project, registers for LED control, the DSP mode, as well as a build information register are added.
The latter holds information about the build date and -time of the IPs, and is particularly time-consuming because of the implementation of the respective drivers to convert the date format in both variants.
In contrast, the addition of the LED control and DSP mode registers is simple and fast, because of the auto-generated code in HLS and VHDL with usage of the register engine.
The single bits in the LED control register directly represent the LEDs' values on the hardware.
The DSP mode register can select the regular FM radio mode and a pass-through mode, which simply forwards the streaming data without any processing.
Summing up, the addition of registers to the design can be time-consuming in both variants, depending on the required driver functionality.
However, the general tendency is that VHDL requires more time, because of this driver issue.

\subsubsection{FIR Filter}

with TB

@@

VHDL: counter that only forwards one when valid, every n samples\\
HLS: consume and process n, before one output (understand blocking AXI stream)

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Integration}
% - IP generation and integration into Vivado
% - Another manual step in VHDL is the addition of the AXI bus interfaces to the IP.
% - Issue: HLS driver import did not work - Vivado SDK is a mess (bad UI based on Eclipse, has bugs, no error output, etc...)

%%%%%%%%%%%%%%%%%%%%
\subsection{Hardware Utilization}
% --> utilization reports
